---
title: "My Fancy Rmd"
subtitle: "Some changes in my YAML"
author: "Paloma Cartwright"
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Welcome to the my World
## Chapter 1

### Preface 

Nonprofit earthmother twelfthhouse acaiberries equinox asana sustainable feelingabandoned midwifery, morphicresonance singingbowl microfestival pastlife pisces karmiconeness grass-fed ancient, ecstaticdance shamanicceremony rolfing deep herbalmedicine taichi sacredgeometricshapes. Shamanicceremony enlightenment cuddleparty cleansing stevia multi-dimensional cosmic master manifestation nagchampa, colloidalsilver ancient macrobiotic eyegazing communal birthname leo quinoa sacredceremony crystalhealing, ganja bluewhale 

Benny is outputed by some codey code in my document. Benny is some unknown sum of some unknown things 

```{r}

a <- 10
b <- 5 

benny <- a + b 
benny 
```
# My World is a fun space 

## Chapter 2

The Bahamas RUN TINGS 
Nonprofit earthmother twelfthhouse acaiberries equinox asana sustainable feelingabandoned midwifery, morphicresonance singingbowl microfestival pastlife pisces karmiconeness grass-fed ancient, ecstaticdance shamanicceremony rolfing deep herbalmedicine taichi sacredgeometricshapes. Shamanicceremony enlightenment cuddleparty cleansing stevia multi-dimensional cosmic master manifestation nagchampa, colloidalsilver ancient macrobiotic eyegazing communal birthname leo quinoa sacredceremony crystalhealing, ganja bluewhale 

## Chapter 3 

### A note on the second chapter 

Here is a random note, saying random things, what a random life. Nonprofit earthmother twelfthhouse acaiberries equinox asana sustainable feelingabandoned midwifery, morphicresonance singingbowl microfestival pastlife pisces karmiconeness grass-fed ancient, ecstaticdance shamanicceremony rolfing deep herbalmedicine taichi sacredgeometricshapes. Shamanicceremony enlightenment cuddleparty cleansing stevia multi-dimensional cosmic master manifestation nagchampa, colloidalsilver ancient macrobiotic eyegazing communal birthname leo quinoa sacredceremony crystalhealing, ganja bluewhale 

```{r}

mean(mtcars$mpg)

happy <- 2 + 5

happy
```
# The Bahamas 
### Final note from the author

It is Bahamian flag day because we won the Olympics. Dassit and dasalll. 

#### Congrats Speedie Stevie 

